New first figure

### 2021-02-17 manuscript/bef_stability/appendixB.Rmd
Advance review

---
title: Appendix B of Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
date: \today 
output:
  pdf_document:
    fig_caption: true 
    keep_tex: true
    toc: true
fontsize: 12pt
header-includes:
   -  \newcommand{\beginsupplement}{\setcounter{table}{2}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}} 
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{float}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
---

@@

Diet information were obtained from fishbase.org and literature (Appendix a, Table S2). The
diet information contained from two to three life stages by species, the life
stages being defined by the body size of the fishes. Over the 57 fish species,
only seven had a piscivorous life stage and only three had a strict piscivorous
life stage. Fish species were then largely omnivorous.

@@

>>>>

---
title: Appendix B of Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
date: \today 
output:
  pdf_document:
    fig_caption: true 
    keep_tex: true
    toc: true
fontsize: 12pt
header-includes:
   -  \newcommand{\beginsupplement}{\setcounter{table}{2}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}} 
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{float}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
number_sections: true
---

@@

Diet information were obtained from fishbase.org and literature (Appendix A, Table S2). The
diet information contained from two to three life stages by species, the life
stages being defined by the body size of the fishes. Over the 57 fish species,
only seven had a piscivorous life stage and only three had a strict piscivorous
life stage. Fish species were then largely omnivorous.

@@

```{r}
metaweb_caption <- paste0(
  "The metaweb which describes the interarctions between all the 412 trophic species, each is
  represented by a node and each color represents a species (S = 45). The seven
  resource nodes (7) are drawn in grey. The species names corresponding to the
  three digit codes are found in Table S1."
)
```

```{r metaweb, fig.cap=metaweb_caption}
knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "metaweb.png"))
```

### 2021-02-17 manuscript/bef_stability/fig1_biomass_network.Rmd
Advance review

source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "local_network_build.R"))
theme_set(theme_cowplot())
.pardefault <- par()
```

```{r}
myload(community_metrics, op_analysis, sem_data, dir = mypath("data"))
community_metrics %<>%
    left_join(select(op_analysis, station, opcod, year))

```

@@

  test %<>%
    mutate(sp_tibble = map(sp_vector, ~tibble(species = names(.x), biomass_sp = .x))) %>%
    unnest(sp_tibble) %>%
    mutate(bm_std_sp = biomass_sp / surface) %>%
    select(station, year, species, bm_std_sp)

@@

  return(test)
}
get_network_summary <- function (com = NULL, station = NULL) {

@@

  label <- paste(
    "S =", tmp$bm_std_stab, ", ",
    "sync =", tmp$sync, ", ",
    "CVsp =", tmp$cv_sp, ", ",
    "\n",
    "R =", tmp$rich_tot_std, ", ",
    "C =", tmp$ct, ", ",
    "Tlvl= ", tmp$t_lvl
  )

@@

plot_dyn_web  <- function (com = NULL, sem_df = NULL, station = NULL, stacked =
  FALSE, .log = FALSE, color_species = NULL) {

@@

  # Make it professional:
  p <- p +
    labs(y = "Biomass density (g by square meter)", x = "Year")

@@

    label <- get_network_summary(com = sem_df, station = station) 
    p <- p +
    annotate("text", x = median(total_bm$year),
      y = max(total_bm$bm_std_sp) + max(total_bm$bm_std_sp) * 5/100, label = label)
  }

@@

  if (!is.null(color_species)) {
    p %<>%
      scale_fill_manual(values = meta_node_color) +
      scale_color_manual(values = meta_node_color)
  }

@@

}
```

```{r}
plot_dyn_web(com = community_metrics, station = 1755, stacked = TRUE, sem_df = sem_data)
plot_dyn_web(com = community_metrics, sem_df = sem_data, station = 1755)
```

@@

  # Get bm
  net <- net %>%
    filter(station %in% st) %>%
    dplyr::select(year, composition) %>%
    unnest(cols = c(composition))  %>%
    select(year, sp_class, bm_std)

@@

get_network_temporal_plot <- function (
  net_list = NULL,
  station = NULL,
  selected_years = NULL,
  node_color = NULL,
  scale_node_size = 0.01,
  par_options = par(mar = c(0,0,4,0)),
  add_title = FALSE
  ) {

@@

  for (i in index) {
    if(!is.null(par_options)) {
      par_options
    }
    plot.new()
    PlotWeb(
      TL = net$obs_troph_level_vector[[index[i]]],
      webTL = net$adj_mat[[index[i]]],
      colnode = set_color_nodes(
	node_list = names(net$obs_troph_level_vector[[index[i]]]),
	color_species_resources = node_color),
      abund = set_node_resources_abun(
	node_list = names(net$obs_troph_level_vector[[index[i]]]),
	node_abun = bm$bm[[index[i]]],
	resource_abun = 1
	),
      collink="grey70",
      scale_abun = scale_node_size,
      rel_abun = FALSE

    )
    if (add_title) {
     title(main = paste0(net$year[[index[i]]]))
    }

@@

```{r}
meta_node_color <- set_color_species(node_list = unique(names(unlist(net$obs_troph_level_vector))), species_list = NULL, resource_list = NULL, col_resource = NULL)

p <- get_network_temporal_plot(net_list = network_analysis, station = 1755,
  selected_years = c(1997, 2010, 2018),
  node_color = meta_node_color, scale_node_size = 0.05, par_options = par(mar = c(1,0,1,0)))
```

```{r, fig.width = 10, fig.height = 12, warning = FALSE}
#par(.pardefault)
#par(.pardefault)
test_p <- plot_grid(
  nrow = 2,
  plot_dyn_web(com = community_metrics, sem_df = sem_data, stacked = TRUE, station = 1755) +
    scale_fill_manual(values = meta_node_color) +
    scale_color_manual(values = meta_node_color)
    ,
  plot_grid(plotlist = p, nrow = 1),
  rel_heights = c(1, 1),
  align = "v"
)

test_p
save_plot(
  "figs/test_temporal_plot.png", test_p,
  nrow = 2, 
  ncol = 1,
  base_height = 4,
  base_width = 8)
```

```{r, eval = FALSE}
test2 <- ggdraw(
  plot_dyn_web(com = community_metrics, sem_df = sem_data, stacked = TRUE, station = 1755)) +
   draw_plot(gg[[1]], .45, .45, .5, .5)

save_plot("figs/test_temporal_plot.png", test2)
```

```{r}
sem_data %>%
  arrange(richness_med, desc(biomass_stab)) %>%
  filter(richness_med >= 3)

```

```{r}
st <- 21604
te <- plot_dyn_web(com = community_metrics, sem_df = sem_data, station = st, stacked = TRUE)
ti <- get_adj_net_station(net = network_analysis, station = st)

meta_node_color <- set_color_species(
  node_list = unique(names(unlist(ti$obs_troph_level_vector))), 
  species_list = NULL,
  resource_list = NULL,
  col_resource = NULL)

p <- get_network_temporal_plot(net_list = network_analysis, station = st,
  selected_years = c(2007, 2010, 2016),
  node_color = meta_node_color, scale_node_size = 0.02, par_options = par(mar = c(0,0,0,0)))
plot_grid(plotlist = p)

for (i in seq_along(p)) {
  save_plot(paste0("figs/test_net", i, ".png"), p[[i]], base_height = 4, base_width = 4)
}
```

```{r}
test_inc <- ggdraw(te + theme(plot.margin = margin(0, 0, 3, 0, "cm"))) +
  draw_plot(p[[1]], .15, -.01, .2, .2)

  save_plot(paste0("figs/test_net_inc", ".png"), test_inc, base_height = 4)
```

>>>>

source(mypath("R", "misc.R"))
source_dir(mypath("R"))
theme_set(theme_cowplot())
.pardefault <- par()
```

```{r}
myload(community_metrics, op_analysis, sem_data, dir = mypath("data"))
community_metrics %<>%
    left_join(dplyr::select(op_analysis, station, opcod, year))
```

@@

  test %<>%
    mutate(sp_tibble = map(sp_vector, ~tibble(species = names(.x), biomass_sp = .x))) %>%
    unnest(sp_tibble) %>%
    mutate(bm_std_sp = biomass_sp / surface) %>%
    dplyr::select(station, year, species, bm_std_sp)

@@

  return(test)
}
get_network_summary <- function (com = NULL, station = NULL, stab = TRUE, com_avg = TRUE) {

@@

  label_stab <- c(
    "Stability" = tmp$bm_std_stab,
    "Synchrony" = tmp$sync, 
    "CVsp" = tmp$cv_sp,
    "Median total biomass" = tmp$prod_std #"' * (g/m^2) * '"
    )
  label_com <- c(
    "Median species richness" = tmp$richness_med,
    "Median connectance" = tmp$ct,
    "Median avg trophic level" = tmp$t_lvl
  )
  label <- NULL

  if (stab) {
    label <- c(label, label_stab)

  if (com_avg) {

    label <- c(label, label_com)

@@

plot_dyn_web  <- function (
  com = NULL, sem_df = NULL, station = NULL,
  stacked = FALSE, .log = FALSE, color_species = NULL, label = NULL,
  label_parsed = FALSE, label_size = 4.5, y_label = NULL, my_ylim = NULL) {

@@

  if ( !is.null(my_ylim) ) 
  {
    p <- p +
      ylim(my_ylim)
  }

  # Make it professional:
  p <- p +
    labs(y = expression(Biomass~density~(g/m^2)), x = "Year")

@@

    label <- get_network_summary(com = sem_df, station = station) 
  }

  if (!is.null(label)) {

    if (is.null(y_label)) {
      y_label <- max(total_bm$bm_std_sp) + max(total_bm$bm_std_sp) * 5/100
    }

    p <- p +
    annotate("text", x = median(total_bm$year),
      y = y_label,
      label = label, parse = label_parsed, size = label_size)
  }

@@

  if (!is.null(color_species)) {
    p <- p + 
      scale_fill_manual(values = color_species) +
      scale_color_manual(values = color_species)
  }

@@

get_label_from_named_vector <- function ( label = NULL, collapse = "\n") {
  paste0(names(label), " = ", label, collapse = collapse)
} 
```

```{r}
label <- get_network_summary(com = sem_data, station = 1755)
lab <- get_label_from_named_vector(label = label[1:4])
plot_dyn_web(com = community_metrics, station = 1755, stacked = TRUE, label =
 lab, label_size = 4.5 )
plot_dyn_web(com = community_metrics, station = 1755, label = lab)
```

@@

  # Get bm
  net <- net %>%
    filter(station %in% st) %>%
    dplyr::select(year, composition) %>%
    unnest(cols = c(composition))  %>%
    dplyr::select(year, sp_class, bm_std)

@@

get_network_temporal_plot <- function (
  net_list = NULL,
  station = NULL,
  selected_years = NULL,
  node_color = NULL,
  scale_node_size = 0.01,
  par_options = par(mar = c(0,0,4,0)),
  add_title = FALSE,
  rel_abun = FALSE,
  log_abun = FALSE
  ) {

@@

  for (i in index) {
    if(!is.null(par_options)) {
      par_options
    }
    plot.new()
    PlotWeb(
      TL = net$obs_troph_level_vector[[index[i]]],
      webTL = net$adj_mat[[index[i]]],
      colnode = set_color_nodes(
	node_list = names(net$obs_troph_level_vector[[index[i]]]),
	color_species_resources = node_color),
      abund = set_node_resources_abun(
	node_list = names(net$obs_troph_level_vector[[index[i]]]),
	node_abun = bm$bm[[index[i]]],
	resource_abun = 1
	),
      collink="grey70",
      scale_abun = scale_node_size,
      rel_abun = rel_abun,
      log_abun = log_abun
    )
    if (add_title) {
     title(main = paste0(net$year[[index[i]]]))
    }

@@

```{r}
```

```{r, fig.width = 10, fig.height = 5, warning = FALSE}
#par(.pardefault)
#par(.pardefault)

p <- get_network_temporal_plot(net_list = network_analysis, station = 1755,
  selected_years = c(1997, 2010, 2018),
  node_color = meta_node_color, scale_node_size = 0.04, par_options = par(mar = c(0,0,0,0)))
#low <- plot_grid(plot_grid(plotlist = gg, nrow = 1), NULL, rel_width= c(1, .1))
low <- plot_grid(plotlist = p, nrow = 1)
test_p <- plot_grid(
  nrow = 2,
  plot_dyn_web(com = community_metrics, sem_df = sem_data, stacked = TRUE, station = 1755) +
    scale_fill_manual(values = meta_node_color) +
    scale_color_manual(values = meta_node_color)
    ,
  low,
  rel_heights = c(1, .6),
  align = "h"
)
test_p
save_plot(
  "figs/test_temporal_plot.png", test_p,
  nrow = 2, 
  ncol = 1,
  base_height = 4,
  base_width = 7)
```

```{r}
first_st <- sem_data %>%
  arrange(richness_tot, desc(biomass_stab)) %>%
  filter(richness_tot >= 2)

tes <- map(first_st$station[1:12], ~plot_dyn_web(
    com = community_metrics,
    sem_df = sem_data,
    station = .x,
    stacked = TRUE))
plot_grid(plotlist = tes)
```

```{r}
first_st$station[5]
#11432 my choice
```

```{r}
last_st <- sem_data %>%
  arrange(desc(prod), biomass_stab ) %>%
  filter(richness_tot < 15)

tes <- map(last_st$station[1:12], ~plot_dyn_web(
    com = community_metrics,
    sem_df = sem_data,
    station = .x,
    stacked = TRUE))
plot_grid(plotlist = tes)
```
```{r}
last_st$station[5]
#6268 my choice
```

```{r pca}
myload(habitat_press, dir = mypath("data"))
library(sf)
library(ggspatial)
# map
myload(p_st, dir = mypath("manuscript", "bef_stability", "figs"))
# Station
myload(biomass_ts_sax, op_analysis, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
station <- get_basin_station(sf_obj = TRUE)
station %<>%
  filter(station %in% unique(op_analysis$station))
## Get bbb
station %<>%
  mutate(type = ifelse(
      station %in% unique(op_analysis_bbb$station),
      "stable", "unstable"),
    st_temporal = ifelse(station %in% qt_station$station, TRUE, FALSE)
  )

habitat_press %<>% na.omit()
mask <- names(habitat_press) %in% names(get_pca_var_name_replacement())

qt_station <- sem_data %>%
  filter(station %in% c(first_st$station[5], last_st$station[5])) %>%
  dplyr::select(station, bm_std_stab)
mysave(qt_station, dir = mypath("data"), overwrite = TRUE)

p_st <- p_st + 
  theme_void() +
  theme(plot.margin = theme_get()$plot.margin, legend.position = "none")

p_st2 <- p_st +
  geom_sf(data = filter(station, type == "stable"), color = "black") +
  geom_sf(data = filter(station, station %in% qt_station$station),
    color = "red", size = 3) +
  geom_sf_text(data = filter(
      station, station %in% qt_station$station
      ), 
    aes(label = c("C", "D")),
    #color = "red",
    fontface = 2,
    size = 5,
    nudge_x = c(-30000, 30000),
    nudge_y = c(30000, -30000)
    ) +
  coord_sf(
    xlim = c(60000, 1100000),
    ylim = c(6100000, 7122216),
    datum = sf::st_crs(2154),
    crs = 2154,
    expand = FALSE
  )

pca_rotated <- compute_rotated_pca(
  .data = habitat_press[, mask],
  naxis = 2
)
p1 <- my_pca_plot(.data = pca_rotated$rotated,
  xaxis = "RC1", yaxis = "RC2", ctb_thld = .4, 
  label_size = 4, force_pull = 0.01, force = 10,
  seed = 1
)

cow_p1 <- plot_grid(NULL, p1, NULL, ncol = 1, rel_heights = c(.02, 1, .02))
fig1ab <- plot_grid(p_st2, cow_p1, ncol = 2, 
  labels = c("A", "B")
)
save_plot(mypath("manuscript", "bef_stability", "figs/fig1ab.png"), fig1ab,
  nrow = 1, 
  ncol = 2,
  base_height = 4,
  base_width = 4
)
``` 
```{r set-up}
st <- c(first_st$station[5], last_st$station[5]) 
library(viridis)
library(ggsci)
library(RColorBrewer)
display.brewer.pal(n = 8, name = 'Dark2')
display.brewer.pal(n = 8, name = 'Set2')

brew_col <- c(brewer.pal(n = 8, name = "Dark2"), brewer.pal(n = 8, name = "Set2"))

ti <- get_adj_net_station(net = network_analysis, station = st)
node_list <- unique(names(unlist(ti$obs_troph_level_vector)))

# Color
meta_node_color <- set_color_species(
  node_list = node_list, 
  species_list = NULL,
  resource_list = NULL,
  col_resource = NULL)
fish_node_mask <- str_detect(names(meta_node_color), "[A-Z]{3}")
meta_node_color[fish_node_mask] <- brew_col[1:sum(fish_node_mask)]
meta_node_color <- c(meta_node_color, PHX = brew_col[length(brew_col)])

#y max:
ymax <- community_metrics %>%
  filter(station %in% st) %>%
  summarise(bm = max(bm_std)) %>%
  deframe 
ymax <- round(ymax * .1) * 10
my_y_label <- ymax - 7 
my_label_size <- 4

```
```{r low-rich-high-stab}

# Label
label <- get_network_summary(com = sem_data, station = st[1])
lab <- get_label_from_named_vector(label = label[1:5])

te <- plot_dyn_web(
  com = community_metrics,
  label = lab,
  y_label = my_y_label,
  label_size = my_label_size,
  my_ylim = c(0, ymax),
  station = st[1],
  stacked = TRUE,
  color = meta_node_color)
p <- get_network_temporal_plot(net_list = network_analysis, station = st[1],
  selected_years = c(1997, 1999, 2002),
  node_color = meta_node_color, scale_node_size = 0.06,
  par_options = par(mar = c(0,0,0,0)),
  log_abun = TRUE
)
#g <- map(p, ggdraw)
#g <- plot_grid(g[[1]], NULL, g[[2]], NULL, g[[3]], nrow = 1, rel_width = c(1, -.2, 1, -.2, 1))
g <- plot_grid(plotlist = map(p, ggdraw), nrow = 1)

cow_te  <- te +
  theme(legend.position = "none")
fig1c <- plot_grid(
  cow_te,
  g,
  nrow = 2,
  align = "h",
  rel_heights = c(1, .6)

)
fig1c
save_plot("figs/fig1c_low_rich.png", fig1c,
  nrow = 2, 
  ncol = 1,
  base_height = 4,
  base_width = 7
)
```

```{r}
# Label
label2 <- get_network_summary(com = sem_data, station = st[2])
lab2 <- get_label_from_named_vector(label = label2[1:5])

te2 <- plot_dyn_web(
  com = mutate(community_metrics, year = as.integer(year)),
  label = lab2,
  y_label = my_y_label,
  label_size = my_label_size,
  my_ylim = c(0, ymax),
  station = st[2],
  stacked = TRUE,
  color = meta_node_color) +
scale_x_continuous(breaks = c(1995, 1998, 2001, 2004))
p2 <- get_network_temporal_plot(net_list = network_analysis, station = st[2],
  selected_years = c(1997, 1999, 2002),
  node_color = meta_node_color, scale_node_size = 0.05,
  par_options = par(mar = c(0,0,0,0)),
  log_abun = TRUE
)
#g <- map(p, ggdraw)
#g <- plot_grid(g[[1]], NULL, g[[2]], NULL, g[[3]], nrow = 1, rel_width = c(1, -.2, 1, -.2, 1))
g2 <- plot_grid(plotlist = map(p2, ggdraw), nrow = 1)

# get legend
cow_te2 <- te2 + theme(legend.position = "bottom") +
  guides(
    fill = guide_legend(nrow = 2, title = "Species"),
    color = guide_legend(nrow = 3, title = "Species")
  )
leg_species <- get_legend(cow_te2)
cow_te2 <- te2 + theme(legend.position = "none")

fig1d <- plot_grid(
  cow_te2,
  g2,
  nrow = 2,
  align = "h",
  rel_heights = c(1, .60)

)
save_plot("figs/fig1d_high_rich.png", fig1d,
  nrow = 2, 
  ncol = 1,
  base_height = 4,
  base_width = 7
)
```

```{r}
cow_fig1ab <- plot_grid(
  p_st2 + theme(panel.background = element_rect(fill = "white")),
  p1, NULL,
  rel_widths = c(.5, .5, .07),
  ncol = 3,
  labels = c("A", "B", ""))
fig1cd <- plot_grid(fig1c, fig1d, ncol = 2, labels = c("C", "D"))
cow_leg_species <- plot_grid(NULL, leg_species, NULL, nrow = 1, rel_widths = c(.25, .5, .25))
fig1 <- plot_grid(cow_fig1ab, fig1cd, cow_leg_species,
  nrow = 3,
  rel_heights = c(.35, .60,.05),
  align = "h"
)
# ele: single column (82 mm), two-thirds page width (110 mm) or full page width (173 mm)
dev.new(width = 8.2, height = 11.0, units = "cm")
# i3: mod + shift + space

# Draw connectance and average trophic level:
lab_net <- get_label_from_named_vector(label = label[6:7])
lab2_net <- get_label_from_named_vector(label = label2[6:7])
fig1_draw <- ggdraw(fig1) +
  draw_label(lab_net, x = .25, y = .075, size = 11) +
  draw_line(
    x = c(0.01, 0.01, 0.49, .49),
    y = c(.11, 0.1, 0.1, .11),
    color = "black", size = 1
  ) + 
  draw_label(lab2_net, x = .75, y = .075, size = 11) +
  draw_line(
    x = c(0.52, 0.52, 0.98, .98),
    y = c(.11, 0.1, 0.1, .11),
    color = "black", size = 1
  )

test <- ggdraw(fig1)
for(i in seq(0,1, .02)) {
  test <- test +
  draw_line(x = c(0, 1), y = c(i , i), color = "black", size = .5) +
  draw_line(x = c(i, i), y = c(0 , 1), color = "black", size = .5)
}
for(i in seq(0,1, .1)) {
  test <- test +
  draw_line(x = c(0, 1), y = c(i , i), color = "red", size = 1) +
  draw_line(x = c(i, i), y = c(0 , 1), color = "red", size = 1)
}

fig1_draw_test <- fig1_draw +
  draw_line(
    x = c(0.1, 0.16),
    y = c(0.26, 0.325),
    color = "black", size = 1
  ) +
  draw_line(
    x = c(0.26, 0.24),
    y = c(0.26, 0.325),
    color = "black", size = 1
  ) +
  draw_line(
    x = c(0.43, 0.34),
    y = c(0.26, 0.325),
    color = "black", size = 1
  ) +
  draw_line(
    x = c(0.59, 0.69),
    y = c(0.26, 0.325),
    color = "black", size = 1
  ) +
  draw_line(
    x = c(0.76, 0.77),
    y = c(0.26, 0.325),
    color = "black", size = 1
  ) +
  draw_line(
    x = c(0.93, 0.89),
    y = c(0.26, 0.325),
    color = "black", size = 1
  )

save_plot(mypath("manuscript", "bef_stability", "figs/fig1.png"), fig1_draw_test,
nrow = 3, 
  ncol = 1,
  base_height = 4,
  base_width = 10 
)
```
